Untitled

### 2018-09-27 PaperCode.Rmd
Pre-submission work
The changes made just before submission to the journel

@@

@@

```{r}
DataCover <-DATAdf  %>%
                #filter(is.na(MSOA11CD)) %>%
  summarise(
           'LADs' = length(unique(DATAdf$LAD11CD)), 
           '% of all LADs' = length(unique(DATAdf$LAD11CD))/length(unique(EW2$LAD11CD))*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

DataCover

xtable(DataCover, caption="Summary of collected data coverage",
       label = "tab:DataCover") %>% 
  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))

rm(DataCover)

@@

sum(LostLowUse$Lost)
```

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020, AffordClass) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032, AffordClass) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class, CountryClass) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio1") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

@@

```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighVal)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighVal.pdf")

@@

#Empty Homes tax

@@

EmptyTax <- LADMean %>% 
  left_join(., QRC2017)%>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(Pop = sum(Pop))) %>%
  mutate(EmptyTax = LowUse*LowUseMean*.01,
         EmptyOfCouncil = EmptyTax/CouncilTax,
         TaxPop = EmptyTax/Pop)

@@

@@

#Rural Analysis

The rural areas seem to be much less likely to had a negative mean difference,  but there is not enough data for the data to be used for moddelling
```{r}
LADrural <- rural %>% group_by(LAD11CD, Urban) %>%
  summarise(count = n()) %>%
  spread(key = Urban, value = count, fill = 0) %>%
  mutate(UrbanPerc = Urban/(Urban+Rural),
         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
  left_join(LADMean,.)

MSOArural <- rural %>% group_by(MSOA11CD, Urban) %>%
  summarise(count = n()) %>%
  spread(key = Urban, value = count, fill = 0) %>%
  mutate(UrbanPerc = Urban/(Urban+Rural),
         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
  left_join(MSOAMean,.)

#Almost no rural areas are classified as having a negative median difference
table(LADrural$Class,LADrural$MedianDiff>0.5)
table(LADrural$Class,LADrural$LowUseType)
2/26
42/86

table(ifelse(percent_rank(LADrural$TourismDensity)>0.5, "HighTour", "LowTour"),LADrural$HighLUP,LADrural$Class)

LADrural  %>%
  ggplot(aes(x = log(LowUsePerc), y =  log(TourismDensity), colour = Class)) + geom_point()

rm(LADrural);rm(MSOArural);rm(rural)
```

@@

```{r}
MSOAAffordRatio <- MSOAMean %>%
  left_join(select(MSOAtoLAD, MSOA11CD, Region), by ="MSOA11CD")

cor(MSOAMea)

MSOAAffordRatio  <- bind_rows(MSOAAffordRatio %>% filter(Region != "London") %>% mutate(type = "Excluding London"), 
                    MSOAAffordRatio %>% mutate( type = "Including London"),
                    MSOAAffordRatio %>% filter(Region == "London") %>% mutate( type = "Only London")) %>%
    group_by(type) %>%
    mutate(
      decile = ntile(AffordRatio, 100)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n(),
              AffordRatio= mean(AffordRatio)
              )

@@

#The plot of the theoretical curves
data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_line() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")

@@

LADModTab <-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
 # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,3))

LADModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
  slice(c(2,8,10)) %>%
  xtable(., caption="Summary of viable Local authority models",
       label = "tab:LADmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"))

@@

MSOAModTab <- MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  mutate(ModelID = rep(1:4,2))

MSOAModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
  slice(c(4)) %>%
  xtable(., caption="Summary of viable MSOA authority models",
       label = "tab:MSOAmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"))

@@

bind_rows(LADMODOut %>% mutate(type = "Financialised LAD"),
          LADMODOut3 %>% mutate(type = "Highly Financialised LAD"),
          LADMODOut2 %>% mutate(type = "High LUP % LAD"),
          MSOAMODOut %>% mutate(type = "High LUP % MSOA")
) %>%
  ggplot( aes(x = term, y = estimate, fill = term)) + geom_boxplot()+
  facet_wrap(~type)+
    theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))
SaveFig("ModelCoeffs.pdf")

@@

FormulaBootLAD<-as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2)

ModPreds <- c("HighVal", "HighLUP", "HighFinance") %>%
  map(~{

EWMod <- LADMean %>% 
  rename_(Reference = .x )  %>% 
  mutate(Reference = as.factor(Reference)) %>%
      glm(formula = FormulaBootLAD, data = ., family=binomial(link='logit'))

    PredictData  %>%
      predict(EWMod, newdata = ., type = "response" ) %>%
      as.tibble(.) %>% setNames(.x)

@@

PopAffected %>% 
  select(PopPerc, FinancePopPerc) %>%
  gather(key, value) %>%
  mutate(key = ifelse(key == "PopPerc", "Financialised", "Highly Financialised")) %>%
  ggplot(aes(x = value)) + geom_density() +
  facet_wrap(~key, scales = "free_x") +
  labs(title ="Estimate percentage of the Population living in areas with high LUP values",
       x = "Population percentage")
SaveFig("PopulationHighLUP.pdf")

@@

LADShape2 <- WholeCountry %>%
  mutate(HighVal = HighVal>0.5,
         HighLUP = HighLUP>0.5,
         HighFinance = HighFinance>0.5) %>% 
  select(LAD11CD:HighFinance) %>%
  gather(key = Type, value = Status, -LAD11CD) %>%
  mutate(Type = case_when(
    Type =="HighFinance" ~ "Highly Financialized",
    Type == "HighLUP" ~"Large LUP percentage",
    Type == "HighVal" ~"Some Financialization"
  ) %>% as.factor(.) %>% fct_relevel("Highly Financialized", after = 2),
  Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)) %>%
  left_join(LADShape,., by = c("lad14cd" = "LAD11CD")
            ) %>% # Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)
  filter(!is.na(Status))

#plot and save
ggplot(LADShape2) +
  geom_sf(aes(fill = Status)) + 
  facet_wrap(~Type)+
  labs(title = "LUP and financialization status in England and Wales") +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
SaveFig("EWHighValMap.pdf")

@@

>>>>

install.packages("breakDown") provides a plot of the glm!

@@

Palgrave nature inter-discplinary journel
https://www.nature.com/palcomms/for-authors#edboard

poss editors
Dr Lei Wang, manchester Urban
Tim Hall, university winchester

maybe
Trifon I Missov, Max planck demographics

reviewr
Glen Bramley at herriot watt

ian caswell ucl mega journel
Kathrine sharp

Reviewers on plos

search term: data mining
César A Hidalgo
Massachusetts Institute of tech

search term: demography
Celine Rozenblat
University of Lausanne
SWITZERLAND

Heidi Harriman Ewen
University of Georgia
UNITED STATES

The information provided in response to your request is copyright Gateshead Council unless otherwise endorsed. Granting access to this information under the Freedom of Information Act does not permit you to re-use the information provided for commercial purposes, for photocopying or reproduction in any form. If you wish to re-use the information you need to apply for a Licence. You can do this by writing to Tanya Rossington, Information Rights Officer, Corporate Services and Governance, 1st Floor, Civic Centre, Regent Street, Gateshead, NE8 1HH. You may be required to pay a fee or comply with conditions for permitted re-use.

@@

```{r}
#Gives Region Data
#Need to put in region names
DataCover <-
 DATAdf %>% 
   filter(!is.na(MSOA11CD)) %>%
  group_by(LAD11CD) %>%
  summarise(Pop = sum(Pop),
            Homes = sum(Homes),
            LUPs = sum(LowUse),
            LSOA = length(unique(LSOA11CD)),
            MSOA = length(unique(MSOA11CD)),
            Region = first(Region),
            LAD = 1) %>%
  select(-LAD11CD) %>%
  group_by(Region) %>%
  summarise_all(funs(sum)) %>%
  left_join(.,
            MSOAtoLAD %>%
  select(LAD11CD, Region, LAD11NM) %>%
  distinct(LAD11CD, .keep_all = T) %>%
  group_by(Region) %>%
  summarise(LADPerc = n())
) %>% 
  mutate(LADPerc = LAD/LADPerc,
         Region2 = c("North East", "North West", "York and Humber", "West Midlands", "East England", "London", "South East", "South West", "Wales")) %>% 
  arrange(Region)

Total <- DataCover %>% summarise_if(is.numeric, sum) %>%
  mutate(
    Region = "Total",
    LADPerc = LAD/348)

DataCover <-bind_rows(DataCover, Total) %>%
  mutate(LADPerc = round(LADPerc*100)) %>%
  rename(`% of LADs` = LADPerc) %>%
  mutate_if(is.numeric, as.integer)

DataCover 
DataCover %>% mutate(Perc = LUPs/Homes)

xtable(DataCover, caption="Summary of collected dataset",
       label = "tab:DataCover") %>% 
  print(., type="latex", file=file.path(TexTables,"DataCover.tex"), include.rownames=FALSE)

rm(DataCover);rm(Total)

@@

sum(LostLowUse$Lost)

  DATAdf  %>%
                filter(!is.na(MSOA11CD)) %>%
  summarise(
           'LADs' = length(unique(DATAdf$LAD11CD)), 
           '% of all LADs' = length(unique(DATAdf$LAD11CD))/length(unique(EW2$LAD11CD))*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

@@

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020, AffordClass) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032, AffordClass) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class, CountryClass) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio1") +
    facet_wrap(.~Area) +
  ggtitle("Low-Use Property distribution by affordability Quartile")
SaveFig("ClassdiffAllData.pdf")

@@

#Compare the Long term vacants data with the collected data

    test <-file.path(DataFolder, "LT_615.xls") %>%
      read_xls(., sheet = 2, skip = 5) %>%
      set_names(make.names(names(.))) %>%
      select(LAD11CD = New.ONS.code, X2017) %>%
      left_join(select(LADMean, LAD11CD, LowUse),.) %>%
      filter(complete.cases(.))

    cor(test$LowUse, test$X2017)

    test <-file.path(DataFolder, "LT_615.xls") %>%
      read_xls(., sheet = 3, skip = 5) %>%
      set_names(make.names(names(.))) %>%
      select(LAD11CD = New.ONS.code, X2017) %>%
      left_join(select(LADMean, LAD11CD, LowUse),.) %>%
      filter(complete.cases(.))

     cor(test$LowUse, test$X2017)

@@

```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median percent of LUPs", x = "Affordability Rank", y = "log Tourism Rank") +
  guides(colour=guide_legend(title="Above Median"))+
  theme(  legend.position="bottom")
SaveFig("HighLUP.pdf")

bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighVal)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Are LUPs more expensive than homes?", x = "Affordability Rank", y = "log Tourism Density") +
  guides(colour=guide_legend(title="More expensive"))+
  theme(  legend.position="bottom")
SaveFig("HighVal.pdf")

@@

# Tax on Empty Homes

@@

EmptyTax <- LADMean %>% 
  left_join(., QRC2017)%>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(Pop = sum(Pop))) %>%
  mutate(EmptyTax = LowUse*LowUseMean*.01,
         AllPropVal = Homes*HomesMean,
         EmptyOfCouncil = EmptyTax/CouncilTax,
         TaxPop = EmptyTax/Pop)

@@

sum(EmptyTax$EmptyTax*100)/sum(EmptyTax$LowUse)

sum(EmptyTax$AllPropVal)/sum(EmptyTax$Homes)

363/306

@@

@@

```{r}
MSOAAffordRatio <- MSOAMean

MSOAAffordRatio  <- bind_rows(MSOAAffordRatio %>% filter(Region != "E12000007") %>% mutate(type = "Excluding London"), 
                    MSOAAffordRatio %>% mutate( type = "Including London"),
                    MSOAAffordRatio %>% filter(Region == "E12000007") %>% mutate( type = "Only London")) %>%
    group_by(type) %>%
    mutate(
      decile = ntile(AffordRatio, 100)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n(),
              AffordRatio= mean(AffordRatio)
              )

@@

#The plot of the theoretical curves
data_frame(Index = 1:100) %>%
  mutate(`Low Value` = exp(-0.05*(Index))+0.05, 
         `High Value` = (exp(Index/100)-1),
    Total = `Low Value` + `High Value`) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_line() +
  labs(title = "LUP percentage VS affordability ratio",
       x = "Affordability ratio",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")

@@

LADModTab <-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = case_when(
    Dependent=="HighVal"~ "High-Value",
    Dependent == "HighLUP"~ "High-LUP %",
    TRUE ~ "HVHL"
  ) %>% as.factor) %>%
  mutate(ModelID = rep(1:4,3)) %>%
  arrange(Dependent)

LADModTab %>% select(ID = ModelID, Dependent, `Beats Null`=`Beats NULL`, Accuracy=`Mean Accuracy`, PosPred, NegPred, Lift) %>%
  slice(c(2,8,10)) %>% 
  mutate(ID = ifelse(ID == 2, 3, ID))%>%
  xtable(., caption="Summary of viable Local Authority models",
       label = "tab:LADmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"), include.rownames=FALSE)

@@

MSOAModTab <- MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  mutate(Dependent = ifelse(Dependent=="HighLUP", "High-LUP %", "High-Value")) %>%
  mutate(ModelID = rep(1:4,2))

MSOAModTab %>% select(ID = ModelID, Dependent, `Beats Null`=`Beats NULL`, Accuracy=`Mean Accuracy`, PosPred, NegPred, Lift) %>%
  slice(c(4)) %>%
  xtable(., caption="Summary of viable MSOA authority models",
       label = "tab:MSOAmodels") %>% 
  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"), include.rownames=FALSE)

@@

bind_rows(LADMODOut %>% mutate(type = "High-Value (LAD Level)"),
          LADMODOut3 %>% mutate(type = "HVHL (LAD Level)"),
          LADMODOut2 %>% mutate(type = "High-LUP % (LAD Level)"),
          MSOAMODOut %>% mutate(type = "High-LUP % (MSOA Level)")
) %>%
  ggplot( aes(x = term, y = estimate, fill = term)) + geom_boxplot()+
  facet_wrap(~type)+
    theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))
SaveFig("ModelCoeffs.pdf")

@@

FormulaBootLAD<-c(as.formula(Reference ~ TourismDensity + AffordRatio),
  as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2),
                  as.formula(Reference ~ TourismDensity + AffordRatio))

ModPreds <- 1:3 %>%
  map(~{

EWMod <- LADMean %>% 
  rename_(Reference = c("HighVal", "HighLUP", "HighFinance")[.x] )  %>% 
  mutate(Reference = as.factor(Reference)) %>%
      glm(formula = FormulaBootLAD[[.x]], data = ., family=binomial(link='logit'))

    PredictData  %>%
      predict(EWMod, newdata = ., type = "response" ) %>%
      as.tibble(.) %>% setNames(c("HighVal", "HighLUP", "HighFinance")[.x])

@@

PopAffected %>% 
  select(PopPerc, FinancePopPerc) %>%
  gather(key, value) %>%
  mutate(key = ifelse(key == "PopPerc", "High-Value", "High-Value High-LUP%")) %>%
  ggplot(aes(x = value)) + geom_density() +
  facet_wrap(~key, scales = "free_x") +
  labs(title ="Estimate percentage of the Population living in areas with high LUP values",
       x = "Population percentage")
SaveFig("PopulationHighLUP.pdf")

@@

LADShape2 <- WholeCountry %>%
  mutate(HighVal = HighVal>0.5,
         HighLUP = HighLUP>0.5,
         HighFinance = HighFinance>0.5) %>% 
  select(LAD11CD:HighFinance) %>%
  gather(key = Type, value = Status, -LAD11CD) %>%
  mutate(Type = case_when(
    Type =="HighFinance" ~ "High-Value High-LUP",
    Type == "HighLUP" ~"High LUP percentage",
    Type == "HighVal" ~"High-Value LUPs"
  ) %>% as.factor(.) %>% fct_relevel("High-Value High-LUP", after = 2),
  Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)) %>%
  left_join(LADShape,., by = c("lad14cd" = "LAD11CD")
            ) %>% # Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)
  filter(!is.na(Status))

#plot and save
ggplot(LADShape2) +
  geom_sf(aes(fill = Status)) + 
  facet_wrap(~Type)+
  labs(title = "Predicting LUP status across England and Wales") +
   theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
         legend.position="bottom")
SaveFig("EWHighValMap.pdf")

@@

#Miscellaneous

#Gets the info on how conentrated the empty homes are
test <- DATAdf %>%
  arrange(-LowUsePerc) %>%
  filter(!is.na(MSOA11CD)) %>%
  mutate(CumsumLowUse = cumsum(LowUse),
         CumsumHomes = cumsum(Homes),
         CumsumLowUsePerc = CumsumLowUse/sum(LowUse),
         CumsumHomesPerc = CumsumHomes/sum(Homes),
         CumPerc = 1:nrow(.)/nrow(.) )

median(test$LowUsePerc)
mean(test$LowUsePerc)
max(test$LowUsePerc)

test[(c(0.5,2,5)/10) %>% map_dbl(~Position(function(fi) fi <= .x, test$CumPerc, right = TRUE)),] %>%
  select(CumsumLowUsePerc, CumsumHomesPerc, CumPerc)

#Dumps a CSV of all the LADs is not necessary for script and so is commented out, The csv can then be used to add the file names and FOI references
# 
# DATAdf %>%
#   select(LAD11CD, LAD11NM, RGNCD = Region) %>%
#   distinct(LAD11CD, .keep_all = TRUE) %>%
#   left_join(data_frame(RGNCD = c("E12000001", "E12000002", "E12000003", 
# "E12000005", "E12000006", "E12000007", "E12000008", "E12000009", 
# "W99999999"), Region = c("North East", "North West", "York and Humber", 
# "West Midlands", "East England", "London", "South East", "South West", 
# "Wales"))) %>%
#   write_csv(file.path(basewd,"LADsDataRaw.csv"))
